Figures

### 2019-04-30 code/figures.rmd
Added tau2 correlation CIs

```{r transform_effect_and_compute_rma}
#Transform effect sizes to biserial correlations (pearson's correlations as is)
#then compute random effects meta-analyses per effect
#'transform_MA' and 'summarizer' are sourced functions
res <- dat %>% 
  split(.$effect) %>%  #necessary step otherwise the function is applied overall
  map(transform_MA) %>% #apply function each effect in the list
  map_dfr(summarizer, .id = "effect") %>%  #apply function and transform to dataframe
  mutate(r = abs(r)) #Absolute values since we are interested in effect size rather than direction
```

@@

@@

##Figure 3
```{r plot_res, cache = TRUE}

>>>>

##Figure 3
```{r transform_effect_and_compute_rma}
#Transform effect sizes to biserial correlations (pearson's correlations as is)
#then compute random effects meta-analyses per effect
#'transform_MA' and 'summarizer' are sourced functions
res <- dat %>% 
  split(.$effect) %>%  #necessary step otherwise the function is applied overall
  map(transform_MA) %>% #apply function each effect in the list
  map_dfr(summarizer, .id = "effect") %>%  #apply function and transform to dataframe
  mutate(r = abs(r)) #Absolute values since we are interested in effect size rather than direction
```

@@

#Tau2
pear <- function(formula, data, indices){
     d <- data[indices,]
     fit <- cor.test(formula = ~ tau2 + r, data=d)
     return(fit$estimate)
}

bootfit <- boot(data=res, statistic=pear, R=1000, formula= ~ r + tau2)

tau2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))

@@

```{r plot_res, cache = TRUE}
